Data analysis for employee cluster assessment

### 2023-07-12 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Update 03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Restructuring

@@

@@

#### Making clusters visualizations using PCA

@@

#### Creating d for cluster analysis

@@

#### Making clusters  visualizations using PCA of different sizes, but only for `d` and adding specification

@@

>>>>

## Functions {.tabset .tabset-pills}

### Selecting data for cluster analysis

@@

### Making clusters of different sizes

@@

### Making clusters visualizations using PCA

@@

### Creating d for cluster analysis

@@

### Making clusters  visualizations using PCA of different sizes, but only for `d` and adding specification

@@

## Intra-cluster visualizations {.tabset .tabset-pills}

### Elbow

## Inter-cluster visaulizations {.tabset .tabset-pills}

### Two-dimensional groupings
